---
title: "accframe Results"
format: pdf  
execute: 
  warning: false
  message: false
  echo: false
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_knit$set(root.dir = "..")
knitr::opts_chunk$set(
  cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE
)
```

```{r ImportObjects}
source("code/utils.R")
for (exp in EXPERIMENTS) {
  get(glue("{exp}_read_exp_data"))()
  source(glue("code/{exp}_create_result_objects.R"))
} 
```

## Table 1: Honesty Experiment: Descriptive Statistics

### Panel A: Participant-period Level 

```{r HonestyTabDescPartPeriod, results='asis'}
honesty_tab_desc_part_period()%>%
  as_latex() %>%
  center_table()
```

### Panel B: Participant Level

```{r HonestyTabDescPart, results='asis'}
honesty_tab_desc_part(
  vars = c("sum_honesty", "truthful", "all_slack", "cc1_passed", "cc2_passed"),
  var_labels = c("Mean % Honesty", "Always Truthful", "Always All Slack", "Recalls Information Structure", "Recalls Optimal Strategy"),
  var_tests = c("t", "chisq", "chisq", "chisq", "chisq")
)%>%
  as_latex() %>%
  center_table()
```

{{< pagebreak >}}


## Table 2: Does Business Framing Affect the Amount of Budget Slack Claimed?

```{r HonestyTabRegResults, results='asis'}
honesty_tab_regression_results() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 3: Reasons

```{r HonestyTabReasons, results='asis'}
honesty_tab_reasons()%>%
  as_latex() %>%
  center_table()
```

{{< pagebreak >}}


## Figure 1: Average Slack Claimed by True Cost and Condition

```{r HonestyFigClSlackVsTrue, fig.width=8, fig.height=5, fig.align="center"}
honesty_fig_claimed_slack_by_true_cost()
```

{{< pagebreak >}}


## Figure 2: Average % Honest by Period and Condition

```{r HonestyFigByPeriod, fig.width=8, fig.height=5, fig.align="center"}
honesty_fig_by_period()
```

{{< pagebreak >}}


## Table 4: Gift Exchange Experiment: Descriptive Statistics

### Panel A: Dyad-period Level

```{r GiftexTabDescDyadPeriod, results='asis'}
giftex_tab_desc_dyad_period()%>%
  as_latex() %>%
  center_table()
```

### Panel B: Participant Level

```{r GiftexTabDescDyadParticipant, results='asis'}
giftex_tab_desc_participant()%>%
  as_latex() %>%
  center_table()
```

### Panel C: Dyad Level

```{r GiftexTabDescDyad, results='asis'}
giftex_tab_desc_dyad() %>%
  as_latex() %>%
  center_table()
```

{{< pagebreak >}}


## Table 5: Does Contextualization Affect the Wage Paid?

```{r GiftexTabRegResultsWage, results='asis'}
giftex_tab_regression_results_wage() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 6: Does Contextualization Affect the Effort Returned?

```{r GiftexTabRegResultsEff, results='asis'}
giftex_tab_regression_results_effort() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 7: Does Contextualization Affect the Wage Sensitivity of Effort?

```{r GiftexTabRegResultsWageEff, results='asis'}
giftex_tab_regression_results_wage_effort() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 8: Does Contextualization Affect the Participant’s Payoffs?

```{r GiftexTabRegResultsPayoff, results='asis'}
giftex_tab_regression_results_payoff() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 9: Reasons

Panel A: Reasons for Wage Decision

```{r GiftexTabReasonsWage, results='asis'}
giftex_tab_reasons_wage()%>%
  as_latex() %>%
  center_table()
```

Panel B: Reasons for Effort Decision

```{r GiftexTabReasonsEffort, results='asis'}
giftex_tab_reasons_effort()%>%
  as_latex() %>%
  center_table()
```

{{< pagebreak >}}


## Figure 3: Wage by Period and Condition

```{r GiftexFigWageByPeriod, fig.width=8, fig.height=5, fig.align="center"}
giftex_fig_wage_by_period()
```

{{< pagebreak >}}


## Figure 4: Effort by Period and Condition

```{r GiftexFigEffortByPeriod, fig.width=8, fig.height=5, fig.align="center"}
giftex_fig_effort_by_period()
```

{{< pagebreak >}}


## Figure 5: Wage Sensitivity of Effort by Condition

```{r GiftexFigWageEff, fig.width=8, fig.height=5, fig.align="center"}
giftex_fig_wage_effort() 
```

{{< pagebreak >}}


## Table 10: Trust Experiment: Descriptive Statistics

### Panel A: Dyad-period Level

```{r TrustTabDescDyadPeriod, results='asis'}
trust_tab_desc_dyad_period()%>%
  as_latex() %>%
  center_table()
```

### Panel B: Participant Level

```{r TrustTabDescDyadParticipant, results='asis'}
trust_tab_desc_participant()%>%
  as_latex() %>%
  center_table()
```

### Panel C: Dyad Level

```{r TrustTabDescDyad, results='asis'}
trust_tab_desc_dyad()%>%
  as_latex() %>%
  center_table()
```

{{< pagebreak >}}


## Table 11: Does Contextualization Affect the Amount Sent by the Sender?

```{r TrustTabRegResultsInv, results='asis'}
trust_tab_regression_results_inv() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 12: Does Contextualization Affect the Percentage Returned by the Receiver?

```{r TrustTabRegResultsRet, results='asis'}
trust_tab_regression_results_pct_ret() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 13: Does Contextualization Affect the Participants’ Payoffs?

```{r TrustTabRegResultsPayoff, results='asis'}
trust_tab_regression_results_payoff() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 14: Reasons

Panel A: Reasons for Investment Decision

```{r TrustTabReasonsSent, results='asis'}
trust_tab_reasons_sent()%>%
  as_latex() %>%
  center_table()
```

Panel B: Reasons for Dividend Decision

```{r TrustTabReasonsSentBack, results='asis'}
trust_tab_reasons_sent_back()%>%
  as_latex() %>%
  center_table()
```

{{< pagebreak >}}


## Figure 6: Amount Sent by Period and Condition

```{r TrustFigSentByPeriod, fig.width=8, fig.height=5, fig.align="center"}
trust_fig_inv_by_period()
```

## Figure 7: Share Returned by Period and Condition

```{r TrustFigReturnedByPeriod, fig.width=8, fig.height=5, fig.align="center"}
trust_fig_div_share_by_period()
```


