---
title: "Trust experiment with Mistral-7B-Instruct-v0.3"
format: pdf  
execute: 
  warning: false
  message: false
  echo: false
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_knit$set(root.dir = "..")
knitr::opts_chunk$set(
  cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE
)
```

```{r ImportObjects}
source("code/utils.R")
trust_read_exp_data("2024-10-16")
source("code/trust_create_result_objects.R")
```

## Table 1: Trust Experiment: Descriptive Statistics

### Panel A: Dyad-period Level

```{r TrustTabDescDyadPeriod, results='asis'}
trust_tab_desc_dyad_period()%>%
  as_latex() %>%
  center_table()
```

### Panel B: Participant Level

```{r TrustTabDescDyadParticipant, results='asis'}
trust_tab_desc_participant()%>%
  as_latex() %>%
  center_table()
```

### Panel C: Dyad Level

```{r TrustTabDescDyad, results='asis'}
trust_tab_desc_dyad()%>%
  as_latex() %>%
  center_table()
```

{{< pagebreak >}}


## Table 2: Does Contextualization Affect the Amount Sent by the Sender?

```{r TrustTabRegResultsInv, results='asis'}
trust_tab_regression_results_inv() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 3: Does Contextualization Affect the Percentage Returned by the Receiver?

```{r TrustTabRegResultsRet, results='asis'}
trust_tab_regression_results_pct_ret() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 4: Does Contextualization Affect the Participants’ Payoffs?

```{r TrustTabRegResultsPayoff, results='asis'}
trust_tab_regression_results_payoff() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Figure 1: Amount Sent by Period and Condition

```{r TrustFigByPeriod, fig.width=8, fig.height=5, fig.align="center"}
trust_fig_inv_by_period()
```


## Figure 2: Share Returned by Period and Condition

```{r TrustFigReturnedByPeriod, fig.width=8, fig.height=5, fig.align="center"}
trust_fig_div_share_by_period()
```


