---
title: "Gift Exchange Experiment with Mistral-7B-Instruct-v0.3"
format: pdf  
execute: 
  warning: false
  message: false
  echo: false
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_knit$set(root.dir = "..")
knitr::opts_chunk$set(
  cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE
)
```

```{r ImportObjects}
source("code/utils.R")
giftex_read_exp_data("2024-10-22_long")
source("code/giftex_create_result_objects.R")
```

## Table 1: Gift Exchange Experiment: Descriptive Statistics

### Panel A: Dyad-period Level

```{r GiftexTabDescDyadPeriod, results='asis'}
giftex_tab_desc_dyad_period()%>%
  as_latex() %>%
  center_table()
```

### Panel B: Participant Level

```{r GiftexTabDescDyadParticipant, results='asis'}
giftex_tab_desc_participant()%>%
  as_latex() %>%
  center_table()
```

### Panel C: Dyad Level

```{r GiftexTabDescDyad, results='asis'}
giftex_tab_desc_dyad() %>%
  as_latex() %>%
  center_table()
```

{{< pagebreak >}}


## Table 2: Does Contextualization Affect the Wage Paid?

```{r GiftexTabRegResultsWage, results='asis'}
giftex_tab_regression_results_wage() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 3: Does Contextualization Affect the Effort Returned?

```{r GiftexTabRegResultsEff, results='asis'}
giftex_tab_regression_results_effort() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 4: Does Contextualization Affect the Wage Sensitivity of Effort?

```{r GiftexTabRegResultsWageEff, results='asis'}
giftex_tab_regression_results_wage_effort() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Table 5: Does Contextualization Affect the Payoffs?

```{r GiftexTabRegResultsPayoff, results='asis'}
giftex_tab_regression_results_payoff() %>%
  as_latex() %>%
  post_process_reg_table() %>%
  center_table()
```

{{< pagebreak >}}


## Figure 1: Wage by Period and Condition

```{r GiftexFigWageByPeriod, fig.width=8, fig.height=5, fig.align="center"}
giftex_fig_wage_by_period()
```

{{< pagebreak >}}


## Figure 2: Effort by Period and Condition

```{r GiftexFigEffortByPeriod, fig.width=8, fig.height=5, fig.align="center"}
giftex_fig_effort_by_period()
```

{{< pagebreak >}}


## Figure 3: Wage Sensitivity of Effort by Condition

```{r GiftexFigWageEff, fig.width=8, fig.height=5, fig.align="center"}
giftex_fig_wage_effort() 
```
